Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-03-03 additional_files/additional_file_1.tex
Pass text through aspell and correct a few other mistakes; manuscript considered ready, version sent to co-authors for approval

\subsection*{Seed coat luster -- loci \textit{Hps} \textit{B?} and \textit{I}}
\label{sv-gwas-seed-coat-luster}

@@

			\caption[Description of loci associated with the traits studied]%
			{Description of loci associated with the traits studied and -log\textsubscript{10}(\emph{p}) of significant
			signals detected in our study using three different genotypic datasets (SNPs/indels, SVs, \emph{k}-mers).}\\
			\label{signals_table}\\

>>>>

\subsection*{Seed coat luster -- loci \textit{Hps}, \textit{B?} and \textit{I}}
\label{sv-gwas-seed-coat-luster}

@@

			\caption[Description of loci associated with the traits studied]%
			{Description of loci associated with the traits studied and -log\textsubscript{10}(\emph{p}) of significant
			signals detected in our study using three different genotype datasets (SNPs/indels, SVs, \emph{k}-mers).}\\
			\label{signals_table}\\
